%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%--------------------------------------------------------
  \cventry
    {Lead Engineer/ Project Manager} % Job title
    {Criterium Engineers } % Organization
    {Remote} % Location
    {Apr. 2024 - present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Enhanced mobile and web applications using Amazon AWS backend, improving performance, reliability, and user experience.}
        \item {Transitioned state management from React Context to Redux, enabling precise control over DataStore syncs and boosting app efficiency.}
        \item {Improved sync logic, implementing full, partial, and on-demand sync options to optimize performance across varied network conditions.}
        \item {Upgraded the Expo framework and libraries, ensuring compatibility and stability across platforms while managing dependency updates.}
        \item {Streamlined project tracking by creating a new project management system in ClickUp, improving team coordination and sprint documentation.}
        \item {Established testing protocols for functionality and sync reliability across network scenarios, with thorough documentation for maintenance and onboarding.}
      \end{cvitems}
    }


%---------------------------------------------------------
  \cventry
    {Lead Developer/ Owner} % Job title
    {Chief Cornerstone Systems LLC} % Organization
    {Remote} % Location
    {Apr. 2022 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Palmetto Court Site}: Revitalized and enhanced a WordPress-based vacation rental site to improve user engagement, functionality, and overall user experience.}
        \item {\textbf{Person First Consulting Site}: Developed a new, user-friendly website on Wix to support a consulting business specializing in diversity training and career coaching.}
      \end{cvitems}
    }

%--------------------------------------------------------
  \cventry
    {Assistant Instructor} % Job title
    {Fullstack Academy LLC} % Organization
    {Remote} % Location
    {Nov. 2022 - June 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Instruct engineers on engineering technical concepts—focused on the PERN stack, beginning with Javascript fundamentals through to Sequelize, Redux and React Native—software architecture, and debugging strategies}
        \item {Utilize agile practices when managing multiple team projects and implementing overall cohort structure}
        \item {Generate additional resources for students to support the existing curriculum}
        \item {Hold weekly one-on-one meetings with students to assess their progress and communicated the outcome to my instructional team members}
        \item {Create and disseminate documentation including cohort repos, grading and schedule trackers and pre-reading materials}
      \end{cvitems}
    }

%--------------------------------------------------------
  \cventry
    {Missionary} % Job title
    {Youth With A Mission} % Organization
    {Multiple Locations} % Location
    {Aug. 2017 - Mar. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{YWAM Tanzania}: Completed the Discipleship Training School (DTS); Partnered with community leaders to provide effective community development solutions, including: clean water, infant checkups, and medical outreach.} 
        \item {\textbf{YWAM Baltimore}: Facilitated and led multiple community programs and worship events, including:}
        \begin{itemize}
          \item {Abode worship nights}
          \item {Discipleship Training Course}
          \item {One School for artists}
          \item {Bloom + Kindle homeless outreach}
        \end{itemize}
      \end{cvitems}
    }

%--------------------------------------------------------
 \cventry
    {Healthcare Specialist} % Job title
    {United States Army} % Organization
    {Multiple Locations} % Location
    {Feb. 2004 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with multiple command groups in large scale events}
        \item {Streamlined Emergency Management procedures in mass inclement weather/ catastrophic events}
        \item {Supported the Wounded Warrior Command at Walter Reed Army Medical center, advising soldiers and families on the behavioral health options available to them during their stay}
        \item {Supervised Operations Center as NCOIC, providing 24 hours, 7 days a week service including management of the call center}
      \end{cvitems}
    }
    
%---------------------------------------------------------
\end{cventries}
